EVI-resilience fine-scale

### 2018-02-26 analysis/notula/evi_resilience_fine_scale.Rmd
add plot

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("here")
library('dplyr')
library("sf")
library("mapview")
library('tidyverse')

library('broom')
library('pander')
library('lsmeans')
library('effects')
library('gridExtra')
library('WRS2')
library('car')
library('MASS')
library('rcompanion')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
```

@@

grid_arrange_shared_legend(rs, ncol = 1, nrow = 1, position='top')
```

```{r}

>>>>

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("here")
library('dplyr')
library("sf")
library("mapview")
library('tidyverse')
library('lemon')
```

@@

pdf(here::here('/analysis/notula/out', 'evi_vs_bai.pdf'), width=10, height = 6)
grid_arrange_shared_legend(rs, ncol = 1, nrow = 1, position='top')
dev.off()

```{r}
## VAS por aqui CARPINTO #############
